---
title: "HW2"
author: "Tianjian Xie"
date: "2023-02-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**##Ans1:**\
(a)$P = uu' +vv'$\
(b)Since P is the projector of $span(u,v)$, and $u,v$ are orthonormal unit-norm vectors. So the eigenvalues are 1. So SVD is $I_m +I_m$.\

**##Ans2:**\
The QR decomposition of A is $A = QR$, where Q is an orthogonal matrix such that $Q \in R^{m \times n}$, and $Q'Q=I_n$.\
and R is an upper-triangular matrix that $R \in R^{n \times n}$. So we can get $det(A)=det(QR)=det(Q)det(R)$. And by the Gram-Schimidt,\
$R_{j,j}=||A_{*j} - \sum^{j-1}_{i=1} R_{ij} Q_i||_2$, since R is upper-triangular, $det(R)=\prod^n_{j=1}R_{jj}$, and since Q is orthogonal, $det(Q)=1$.\
So $det(A)=|\prod^n_{j=1}R_{jj}|=\prod^n_{j=1}|||A_{*j} - \sum^{j-1}_{i=1} R_{ij} Q_i||_2|\leq\prod^n_{j=1}||A_{*j}||_2$\

**##Ans3:**\
**(a)**\
From given information, we know $|A_{jj}|\geq \sum^m_{i=1,i\neq j}|A_{ij}|$, if $|A_{11}|=0$, $0\geq \sum^m_{i=1,i\neq j}|A_{ij}|$.Conflict.\
Since $L_1 = \begin{pmatrix} 1 & 0_{1,2:m} \\ -A_{2:m,1}\over A_{11} & I_{m-1} \end{pmatrix}$,\
so $L_1A = \begin{pmatrix} 1 & 0_{1,2:m} \\ -A_{2:m,1}\over A_{11} & I_{m-1} \end{pmatrix} \begin{pmatrix} A_{11} & A_{1,2:m} \\ A_{2:m,1} & A_{2:m,2:m} \end{pmatrix}$,\
By matrix multiplication:\
First column is $A_{11}, -A_{2,1}+A_{2,1},-A_{3,1}+A_{3,1},...,-A_{m,1}+A_{m,1}$, which is $A_{11},0,0,...$.\
Second column is $A_{1,2}, {-A_{2,1}\times A_{1,2}\over A_{11}}+A_{2,2} , {-A_{3,1}\times A_{1,3}\over A_{11}}+A_{3,3},...,{-A_{m,1}\times A_{1,m}\over A_{11}}+A_{m,m}$.... and m-th column is $A_{1,m}, {-A_{2,1}\times A_{1,m}\over A_{11}}+A_{2,m},{-A_{3,1}\times A_{1,m}\over A_{11}}+A_{3,m},...,{-A_{m,1}\times A_{1,m}\over A_{11}}+A_{m,m}$.\
So $L_1A = \begin{pmatrix} A_{11} & A_{1,2:m} \\ 0_{2:m,1} & {{-A_{2:m,1}A_{1,2:m}\over A_{11}}+A_{2:m,2:m}} \end{pmatrix}$.\

**(b)**\

**(c)**\
Solve by householder QR decomposition. Since R is upper-triangular, and $A=QR$, say for rank m matrix A, there are orthogonal matrices $L_1,L_2,...,L_{m-1}$ and $Q=L_1'L_2'...L_{m-1}'$.\
Hence $A=L_1'L_2'...L_{m-1}'R$. So $R=L_{m-1}L_{m-2}...L_1A$ is upper-triangular.\
The main points of solving $Ax=b$ is solve $R'y=b$ and $Rx=y$. Since we have QR decomp of A to get R, we can solve x and y.\

**(d)**\
```{r}
m <- seq(100,1000,50)
A <- matrix(c())
```
